\documentclass[a4paper,12pt,fleqn]{article}
\setlength{\parindent}{0em}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{siunitx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{import}
\usepackage{comment}
\usepackage{setspace}

% Unit definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\DeclareSIUnit\kilowatthour{kWh}
\DeclareSIUnit\kilowattpeak{kW_P}
\DeclareSIUnit\kVA{kVA}
\DeclareSIUnit\kVAR{kVAR}
\DeclareSIUnit\year{y}
\DeclareSIUnit\north{N}
\DeclareSIUnit\south{S}
\DeclareSIUnit\second{s}

\begin {document}

\textbf{Question One}

\begin{enumerate}[label=\alph*)]
\begin{doublespace}
\item $\mathrm{HLC (conduction) }=q_C=\sum{U_iA_i}=0.2\times 100+0.2\times 50+0.25\times 80 +1.0 \times 20=\SI{70}{\watt\per\kelvin}$
\item $\mathrm{HLC (infiltration) }=q_A=\frac{nV}{3}=\frac{0.2\times 250}{3}=\SI{16.7}{\watt\per\kelvin}$ using $n\approx\frac{n_{50}}{20}$
\item $\mathrm{HLP}=(q_C+q_A)/\mathrm{TFA}=\frac{70+16.7}{100}=\SI{0.867}{\watt\per\kelvin\per\metre\squared}$
\item $\mathrm{Annual\ Heat\ load}=(q_C+q_A)\times DD \ \frac{24}{1000}=116\times 1800 \times \frac{24}{1000}=\SI{3745}{\kilowatthour}$
\item Factors causing (d) to be too high: Use of intermittent heating; solar and other gains have been ignored.
Factor causing (d) to be too low: houses not built to specification so that $q_C$ and $q_A$ are higher than calculated here.
Actual degree days could differ from 20 year average.
\end{doublespace}
\item 
\begin{align*}
R_T&=\sum{x_i/k_i}=\frac{0.05}{0.7}+\frac{y}{0.055}=\frac{1}{U}=5\\
\intertext{Hence}
\frac{y}{0.055}&=5-\frac{0.05}{0.7}=4.93\\
\intertext{so}
y&=0.055\times 4.93 = \SI{0.27}{\metre}
\end{align*}
\item Heat conduction across the cavity is by conduction, convection and radiation. The radiation contribution is proportional
to the emissivity ($0<\epsilon <1$) of the surfaces.
Low emissivity surfaces such as shiny foil backing can significantly reduce the radiation conduction
\item Credit: Ties bridge(are in parallel with) the air gap. They likely have a high thermal conductivity, however their total cross-sectional
area will be much lower than that of the air in the gap. Thus their overall thermal-short effect is (designed to be) low. 
Credit attempt at demonstrating this by calculation
\item Credit attempts to calculate mass per $m^2$ of each component, using $m=\rho At$ where $A$ is the are fraction and $t$ is the thickness.
\begin{table}[ht]
\caption{Straw bale wall} % title of Table
\centering % used for centering table
\begin{tabular}{c c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
Component & Density & AF & t & m & EE / kg & EE.\\  [0.5ex] %heading
\hline % inserts single horizontal line
Lime & 1600 & 1 & .05 & 80 &  1.03 & 82.4\\% inserting body of the table
Straw & 120 & 1 & 0.27 & 32.4 & 0.24 & 7.8\\
\hline
 & & & & &Total &\SI{90.2}{\mega\joule\per\metre\squared}\\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{table:straw} % is used to refer this table in the text
\end{table}
\item Accept any reasonable choices for materials, dimensions etc.
\begin{table}[ht]
\caption{Concrete block cavity wall} % title of Table
\centering % used for centering table
\begin{tabular}{c c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
Component & Density & AF & t & m & EE / kg & EE.\\  [0.5ex] %heading
\hline % inserts single horizontal line
Concrete & 2300 & .93 & 0.2 & 428 &  0.7 & 299.4\\% inserting body of the table
Mortar & 1900 & 0.07 & 0.2 & 26.6 & 0.97 & 25.8\\
Celotex & 35 & 1 & 0.1 & 3.5 & 101 & 353.5\\
Plasterboard & 700 & 1.0 & 0.0125 & 8.75 & 6.75 & 59.1\\
Plaster dabs & 600& 0.2 & 0.025 & 3 & 1.8 & 5.4\\
Render+skim & 1900 & 1 & .013 & 24.7 & 0.97 & 23.96\\
\hline
 & & & & &Total &\SI{767}{\mega\joule\per\metre\squared}\\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{table:conc} % is used to refer this table in the text
\end{table}
\item For concrete wall, assume travel distance = 200 km - likely the case for the cement fraction. Mass of walls $\approx\SI{0.5}{\tonne\per\metre\squared}$, of which about 10\% is cement, hence transport energy $\approx 200 \times 0.05= \SI{1.0}{\kilowatthour}$. This is much less than the cradle to gate energy of the wall, so transport of this distance is not a major contributor to total embodied energy.
Similar arguments apply to straw wall - credit attempt at quantitative argument, also attempt to assess relative importance of transport energy in whole-life energy of house.
\item $q_C \gg q_A$ hence more effort to improve insulation rather than infiltration will pay greater dividends, providing the measure is cost effective. Increased, managed solar gain, provided it does not lead to a cooling energy cost, could also help. Draft proofing is very cheap and effective.
\item Straw bales reduce embodied energy of walls by $\SI{680}{\mega\joule\per\metre\squared}=\SI{190}{\kilowatthour\per\metre\squared}$, hence by $\SI{19,000}{\kilowatthour}$ in total. This represents less than 4 years worth of in-use energy. However if that energy were reduced still further, this reduction in embodied energy becomes a greater and greater fraction, eventually the dominant fraction, of the whole-life energy.
\end{enumerate}


\textbf{Question Two}
\begin{enumerate}[label=\alph*)]
\item Provides sufficient accessible heat capacity, ideally within the thermal envelope of the building, matched to solar gains, to moderate interior temperature swings in response to external swings.
\item Because mode of transfer of heat to the wall is by convection and conduction, which relies on a temperature gradient being set up  across a boundary, with the surface of the wall at a lower temperature than the bulk temperature of the air.
\item Average temperature rises after 10 hours are $T_1 \approx \SI{4}{\celsius}$ for skin 1 and $T_2 \approx \SI{1}{\celsius}$ for skin 2.
\begin{align*}
E_1 &=mc\Delta T_1\\
&=\rho V c \Delta T_1\\
&=2300\times 0.15\times 840\times \Delta T_1\\
&=\SI{2.9e5}{joule\per\metre\squared\per\celsius}\cdot \Delta T_1\\
&=\SI{1.2}{\mega\joule\per\metre\squared}=\SI{0.32}{\kilowatthour\per\metre\squared}
\end{align*}
and
\begin{align*}
E_2 &=mc\Delta T_2\\
&=\SI{2.9e5}{joule\per\metre\squared\per\celsius}\cdot \Delta T_2\\
&=\SI{0.29}{\mega\joule\per\metre\squared}=\SI{0.08}{\kilowatthour\per\metre\squared}
\end{align*}
\item The second skin stores one quarter the thermal energy after 10 hours, for double the additional mass, thickness, embodied energy and cost.
\item Assuming $\Delta T=\SI{4}{\celsius}$, then after 10 hours the stored thermal energy $\approx 65\times 0.32=\SI{21}{\kilowatthour}$
\item The maximum solar gain per day is $20-\SI{25}{\kilowatthour\per\day}$ this is about equal to what can be absorbed by the skin of blocks in one day, albeit with temperature rise of \SI{4}{\celsius}. If this is too much, then the solar gains needs to be controlled in the summer months, perhaps by use of shades, or by reducing window size, or by using an intermediate space such as a conservatory to directly receive the solar gain.
\item Credit discussion in terms of diffusivity (speed at which comes to thermal equilibrium), and volumetric heat capacity. Granite appears to offer the best combination of these two - so has higher diffusivity than dense concrete, but also just as high a volumetric heat capacity, hence can provide sufficient thermal mass in small volume AND follow diurnal temperature fluctuations. Credit awareness of thickness as potential problem, if granite used.
\item Walls act as thermal store which can have a moderating influence on large climatic temperature swings between night and day. Hence suitable in regions that have such a climate. However in tropical regions, not suitable since temperatures remain high, hence wall will heat up and stay hot, acting as an oven!
\end{enumerate}

\textbf{Question Three}
\begin{enumerate}[label=\alph*)]
\item NuOffice
    \begin{itemize}
        \item Highly insulated
        \item Use of MVHR
        \item PV on roof.
        \item thermochromic windows if facing S, SE or SW - passive solar heating
        \item lower proportion of glazing than in typical office blocks
        \item absorption heat pump for cooling and heating
        \item use of thermal mass = concrete floors and wall, with water channels to distribute heat
        \item Widespread use of sensors, including post-construction monitoring.
        \item Detailed building physics models used
        \item Design solution sought that suited owners and tenants.
        \item In southern climates, additional cooling might be required
        \item Made particular use of locally available ground water (well)
    \end{itemize}
\item Passivhaus
    \begin{itemize}
        \item Highly insulated - credit knowledge of U-value limits
        \item Low permeability $n_{50}< 0.6$ . How is this achieved?
        \item Passive solar heating. How achieved and how managed.
        \item Compact shape. Why?
        \item Focus on primary energy usage - encouragement to use renewables. How?
        \item no emphasis on embodied carbon or energy
        \item no explicit focus on carbon
        \item knowledge of PH metrics.
    \end{itemize}
    These measures can reduce in-use energy and emissions to $< 5\%$ ADL1A house, and over 60 years this cumulative savings greatly outweigh additional embodied energy and emissions due to use of more materials in construction.
\end{enumerate}


\end{document}
